### 2013-01-10 thesis-proposal/problem.tex
Added updated thesis statement and edited intro a bit

\section{Problem}

Designing and implementing a programming language and its supporting tools (collectively, a \emph{programming system}) that simultaneously supports a natural programming style, helps users find and fix errors early, and performs well across diverse problem domains remains a grand challenge in computing. Indeed, it is now widely acknowledged that no simple set of constructs will be able to handle all of the challenges modern computing faces. Consistent with this view, a large number of researchers and domain experts in both research and industry are actively engaged in the design, implementation and analysis of a variety of novel language-based abstractions, compilation strategies and tools targeted at different problem domains.

%In implementing a new feature or abstraction, these experts can take one of several approaches. 
To realize a new feature or abstraction, these experts often take a \emph{language-oriented approach}, whereby the new constructs are developed and distributed together with a new programming language. The flexibility of this approach, coupled with support from tools like compiler generators, has led to a proliferation of specialized languages, each built around a particular set of privileged constructs. Unfortunately, a key issue limiting the practicality of this approach occurs at the boundaries between languages -- specialized constructs particular to one language cannot always be safely and naturally expressed in another, so building a program out of components written in different specialized languages can often prove difficult.

>>>>

\section{Introduction}

Jonathan Aldrich (ISR), chair
Brad A. Myers (HCII)
Robert Harper (CSD)
Premkumar Devanbu (UCSD)

Designing and implementing a programming language together with its supporting tools (collectively, a \emph{programming system}) that simultaneously supports a natural programming style, helps users find and fix errors early, and consistently performs well across diverse application domains remains a grand challenge in computing. Indeed, these concerns are often at odds with one another, so system designers must make trade-offs. No small set of general-purpose constructs can completely satisfy every need. Evidence supporting this view comes from the large community of researchers and domain experts designing new domain-specific languages and tools, each tailored to the needs of a particular developer community or application domain.

%In implementing a new feature or abstraction, these experts can take one of several approaches. 
To realize a new construct, these experts often take a \emph{language-oriented approach}, developing and distributing it together with a new programming language. The flexibility of this approach, coupled with support from tools like compiler generators and language workbenches, has led to a proliferation of specialized languages, each built around a particular set of privileged constructs. Unfortunately, a key issue limiting the practicality of this approach occurs at the boundaries between languages -- specialized constructs particular to one language cannot always be safely and naturally expressed in another, so building a program out of components written in different specialized languages can often prove difficult.
